\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-02 paper.tex
some restracturing to emphasize the case studies early on
refactoring
fix
added 2 authors

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^1$, John Erickson$^2$, Cheng Huang$^3$, Akash Lal$^3$}\\
{\rm Matt McCutchen$^4$, Shaz Qadeer$^3$, Wolfram Schulte$^2$, Paul Thomson$^1$}\\\\
$^1$Imperial College London, $^2$Microsoft, $^3$Microsoft Research\\
$^4$Massachusetts Institute of Technology\\
} % end author

@@

\section{Overview}
\label{sec:overview}

@@

\section{Testing production systems}
\label{sec:method}

@@

\section{Case studies}
\label{sec:cases}

>>>>

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^1$, Shuo Chen$^3$, Alastair F. Donaldson$^1$, John Erickson$^2$, Cheng Huang$^3$}\\
{\rm Akash Lal$^3$, Matt McCutchen$^4$, Shaz Qadeer$^3$, Wolfram Schulte$^2$, Paul Thomson$^1$}\\\\
$^1$Imperial College London, $^2$Microsoft, $^3$Microsoft Research\\
$^4$Massachusetts Institute of Technology\\
} % end author

@@

\section{Distributed Systems}
\label{sec:bg}

@@

\section{Case Studies in Microsoft}
\label{sec:cases}

\section{Testing Production Systems with \psharp}
\label{sec:method}

@@

\section{The \psharp Bug-Finding Runtime}
\label{sec:psharp}

\input{psharp}

\section{Experience Report}
\label{sec:exp}

\input{experience}
